Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-02-19 papers/wdmerger_I/paper.tex
No longer using the graphics showing multi-level Poisson boundary conditions -- should be able to explain it easily enough in the text.
Slightly update description of how we store git commit hashes, consistent with the recent CASTRO changes.

The software used to generate the test problems in this paper
(as well as the paper text itself),
\texttt{wdmerger}\footnote{\url{https://github.com/BoxLib-Codes/wdmerger}},
is freely available at an online repository hosting service.
Version control in both the parent software (BoxLib, CASTRO) and in \texttt{wdmerger}
permits us to reference the state of the code at the time a simulation
was performed. To do so, in all plot files generated we store
the complete set of parameters used in that simulation. We also store the 
version commit hashes of the parent software in the plot files.
We store the commit hashes of all three as comments in the metadata of 
any EPS files generated as figures in this paper.

@@

%\begin{figure}
%  \centering
%  \includegraphics[width=3.1in]{plots/nested2}\hspace{1em}
%  \includegraphics[width=3.1in]{plots/nested3}
%  \caption{\label{fig:2levgrav} Schematic showing the solve for $\phi$ for a 2-level grid.}
%\end{figure}

>>>>

The software used to generate the test problems in this paper
(as well as the manuscript itself),
\texttt{wdmerger}\footnote{\url{https://github.com/BoxLib-Codes/wdmerger}},
is freely available at an online repository hosting service.
Version control in both the parent software (BoxLib, CASTRO) and in \texttt{wdmerger}
permits us to reference the state of the code at the time a simulation
was performed. In all plot files and diagnostic output generated by CASTRO, 
and EPS figure files and plots generated by \texttt{wdmerger} for this work,
we store the active \texttt{git} commit hashes of BoxLib, CASTRO and \texttt{wdmerger}.

@@
